Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-14 Cover_letter_JPM.tex
new Table 1 (merged table 1 and table 2)
Updates from Overleaf

\documentclass[preprint,12pt]{elsarticle}
% Extended revision and answer question (2 reviewers)
% for JPM-1174473
%Since April 19, 2021
%Please resubmit your revised manuscript through the following link:
% https://susy.mdpi.com/user/manuscripts/upload?pre_hash_key=6f6b5248032093559a0cdfda5026f51f

\usepackage[bf]{caption}
\newcommand{\bcaption}[2]{\caption{\textbf{#1} #2}}

@@

% modify on main.tex, marked with
%\begin{MyColorPar}{red}
%\end{MyColorPar}
The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129). Also, it was shown here in the following paragraph.

@@

\subsection*{2-1}%(ok)
% sliding window cutoff selection with FDR corrected
Exploring all possible expression cutoffs is controversial. 
A robust expression biomarker should be effective and detectable at most major cutoffs. Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05). 
For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff. % might be false positive
But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. % true positive
This strategy only identifies more weak “biomarkers,” and it also captures more false positives. % defense (ok) => NOT weak 其實 very significant; 欠一張圖
Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
% (ok) PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity

@@

% 1) 本來就有計算 FDR and excluding >= 0.05 (ok)
% 2) and FDR (done)
We appreciate the reviewer to kindly advise us about the principle of sliding window cutoff selection in detail.
% and give us this nomenclature as "sliding window"
%% *** 準備一張 20 candidates: accumulated \textit{P}-value plots 來說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05
We correct our statement of this workflow (please see Answer 2-2).
There is more evidence to validate them (please see Answer 2-3).

We understand that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (p=0.05).
*** According to our results, all of preliminary biomarkers have FDR-corrected \textit{P} values from 1e-4 to 0.04 whatever grouped by cutoffs at 50\% quantile cutoff or at 70\% quantile cutoff (Please see supplementary Figure SXXX).
There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
Thus we also performed the FDR correction applied on cutoff finding procedure as well as Bonferroni adjustment in candidate filtering.

@@

% and FDR (done; ok)
We also modified the last paragraph of "Cutoff Finder Core Engine" in the Material and Methods section.
%Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction
The caption of Figure 1, Table 1, and Table 2 has description about 1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]

@@

@@

@@

We also modified the last paragraph in the Material and Methods section, and also described "the p-values are affected by the sample size" in the Discussion section.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]

@@

%
\begin{MyColorPar}{blue}
Answer
%(OK)
We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]

@@

We placed more descriptions about researcher's work using TCGA to find expression biomarkers in the Introduction section.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.\\[0.3cm]

@@

% 不要誇大說明 謙虛道歉
We apologize for exaggerating the difficulties of our workflow.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following two paragraphs.

@@

According to the reviewer's comment, the Discussion was modified accordingly. The paragraphs marked in \textcolor{red}{Red} from page 11 (line 257) to page 13 (line 354) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]
%(the revised portions in the manuscript are indicated in \textcolor{red}{red})

>>>>

\documentclass[preprint,12pt]{elsarticle}
% Extended revision and answer question (2 reviewers)
% for JPM-1174473
%Since April 19, 2021
%Please resubmit your revised manuscript through the following link:
% https://susy.mdpi.com/user/manuscripts/upload?pre_hash_key=6f6b5248032093559a0cdfda5026f51f
\usepackage{tikz-imagelabels} % for  tikz
\usepackage{siunitx} % for  1e-10 scientific notation
\usepackage[bf]{caption}
\newcommand{\bcaption}[2]{\caption{\textbf{#1} #2}}

@@

% modify on main.tex, marked with
%\begin{MyColorPar}{red}
%\end{MyColorPar}
The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129). Also, it is shown here in the following paragraph.

@@

\subsection*{2-1}%(ok)
% sliding window cutoff selection with FDR corrected
Exploring all possible expression cutoffs is controversial. 
A robust expression biomarker should be effective and detectable at most major cutoffs. Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05). 
For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff. % might be false positive
But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. % true positive
This strategy only identifies more weak “biomarkers,” and it also captures more false positives. % defense (ok) => NOT weak 其實 very significant; 欠一張圖 => new Figure 4 (ok)
Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
% (ok) PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity

@@

% 1) 本來就有計算 FDR and excluding >= 0.05 (ok)
% 2) and FDR (done)
We appreciate the reviewer to kindly advise us about the principle of sliding window cutoff selection in detail.
% and give us this nomenclature as "sliding window"
%% *** 準備一張 3/20 candidates: accumulated \textit{P}-value plots 來說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05, even < 0.001
We have corrected our statement of this workflow (please see Answer 2-2).
We provide more evidence to validate them (please see Answer 2-3).

We understand that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P}=0.05).
According to our results, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 whatever grouped by cutoffs at 50\% quantile cutoff or at 70\% quantile cutoff (Please see Figure \ref{fig:figure4} in this cover letter; it is also shown in manuscript as updated "Figure 4").
%There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
Thus we performed the FDR correction applied on cutoff finding procedure as well as Bonferroni adjustment in candidate filtering.

% and a new Figure 4
\begin{figure}[hp]

% TCGA FDR Pvalue of CAMK2N1 (1.628308e-05), IL19 ( 6.543871e-06), FCGBP (4.827833e-05)
\setlength{\unitlength}{1cm}
\begin{picture}(15, 20) %(1,0.55038404)%
\centering
  \put(0,0){\includegraphics[width=14cm]{Figure_4_CAMK2N1_IL19_FCGBP.pdf}}%
  \put(2.5, 14.3){\fontfamily{qcr}\selectfont
  \tiny *\textit{P} = \num{1.63e-05}}%CAMK2N1
    \put(2.5, 9.45){\fontfamily{qcr}\selectfont
  \tiny *\textit{P} = \num{6.54e-06}}%IL19
    \put(2.5, 4.55){\fontfamily{qcr}\selectfont
  \tiny *\textit{P} = \num{4.83e-05}}%FCGBP

%\begin{annotationimage}{width=15cm}{Figure_4_CAMK2N1_IL19_FCGBP.pdf}
%\includegraphics[width=15cm]{Figure_4_CAMK2N1_IL19.pdf}
%\draw[annotation left = {Aries at 0.3}]

%\end{annotationimage}
\end{picture}%

\bcaption{Kaplan-Meier survival analyses, by cutoff finding.}
{The Kaplan-Meier curves of (a) CAMK2N1, (c) IL19, and (e) FCGBP under optimal \textit{P} value. 
%((b) the cutoffs derived from it's cumulative \textit{P} value plot).
%(c) Kaplan-Meier plot of IL19 under optimal \textit{P} value;
%((d) the cutoffs derived from it's cumulative \textit{P} value plot).
%(e) Kaplan-Meier plot of FCGBP under optimal \textit{P} value.\\
The cutoffs, in the cumulative \textit{P} value plots of (b) CAMK2N1, (d) IL19, and (f) FCGBP, respectively,
shows that over 50\% of those unadjusted \textit{P} values are below 0.001 derived by sliding-window cutoff finding procedure.\\
* \textit{P}: Adjusted \textit{P} value by \acrfull{fdr}
}
\label{fig:figure4}
\end{figure}

@@

% and FDR (done; ok)
We also modified the last paragraph of "Cutoff Finder Core Engine" in the Material and Methods section.
%Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction
***The caption of Figure 1 and Table 1 has description about 1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

%\end{MyColorPar}

@@

2021/06/13
CAMK2N1, IL19, and FCGBP is validated?
%candidate_fdr100

(please see Figure \ref{fig:hazards3}).

\begin{figure}
    \centering
    \includegraphics[width=13cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_top3FDRKM.pdf}
    \bcaption{Volcano plot of genes under survival analyses of TCGA HNSCC.}{
%X axis: unadjusted \textit{P} value of Kaplan-Meier survival (-log10 transformed).
%Y axis: multivariate hazard ratio from Cox proportional regression model.
%Dotted line: significant Bonferroni corrected \textit{P} value. 
%\textcolor{red}{Red dots} mark 10 genes (unvalidated), which impact on poor prognosis ($HR>=1.5$). \textcolor{green}{Green dots} mark 10 genes (unvalidated), which affect on better survival ($HR<=0.5$).
    This cohort has been applied for exploration of the candidate biomarkers.
    Total 9416 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05.
    \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the other 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.6$.\\
    Remarks:\\
    \textcolor{red}{Red spots}: $HR > 1.0$;
    \textcolor{green}{Green spots}: $HR < 1.0$;\\
    X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);\\
    Y-axis: HR of Cox proportional hazard regression model\\
    }
    \label{fig:hazards3}
\end{figure}

@@

We also modified the last paragraph in the Material and Methods section, and also described "the p-values are affected by the sample size" in the Discussion section.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

%
\begin{MyColorPar}{blue}
Answer
%(OK)
We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

We placed more descriptions about researcher's work using TCGA to find expression biomarkers in the Introduction section.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.\\[0.3cm]

@@

% 不要誇大說明 謙虛道歉
We apologize for exaggerating the difficulties of our workflow.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following two paragraphs.

@@

According to the reviewer's comment, the Discussion was modified accordingly. The paragraphs marked in \textcolor{red}{Red} from page 11 (line 257) to page 13 (line 354) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]
%(the revised portions in the manuscript are indicated in \textcolor{red}{red})

### 2021-06-14 main.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Tex
\usepackage[]{caption} % bf
\newcommand{\bcaption}[2]{\caption{\textbf{#1} #2}}
\usepackage{outlines}
% mark in blue or red
\usepackage{xcolor}
\definecolor{asparagus}{rgb}{0.53, 0.66, 0.42}

@@

The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
The 967 genes were kept by criteria of uncorrected \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.5 or less than 0.5) (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b) multivariate plots). 
At the final step, a stringent criteria (Bonferroni \textit{P} value correction) was used to yield twenty candidates (see Figure \ref{fig:figure2}(c), (d)). 
% before validation
Among these candidates, ten overexpressed genes (symbol as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) are significantly associated with a poor prognosis of  \acrshort{os} (see Table \ref{tab:newTable1}). 
The other ten overexpressed genes (symbol as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival (see Table \ref{tab:newTable1}, with their gene name).
We made a volcano plot for 9416 genes by Kaplan-Meier \textit{P} value (less than 0.05, obtained during cutoff finding procedure) against the Cox hazard ratio (see Figure \ref{fig:figure3}). The plot reveals that the most significant (Bonferroni-adjusted \textit{P} $< 0.05$) candidate genes are located above the dotted line. At the same time, Cox's HR separated them on the two-side with prognostic impact.
% => after validation: The result showed six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are significantly associated with a poor prognosis of overall survival. Furthermore, the four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.

@@

%\subsubsection{Figure 2:h}
\begin{figure}[hp]
\centering
\includegraphics[width=14cm]{Figure2.pdf}
\bcaption{\acrshort{hnscc} Cox's hazard ratio and \textit{P} value plot.}
{(a) Univariate HR versus uncorrected \textit{P} value; (b) Multivariate HR versus uncorrected \textit{P} value; (c) Univariate HR versus Bonferroni corrected \textit{P} value; and (d) Multivariate HR versus Bonferroni corrected \textit{P} value.}
\label{fig:figure2}
\end{figure}

% tables 1  3
%%% tables
% Table1
% wide table \usepackage{tabularx}
% makecell{}

@@

\begin{table}[ht]
\centering
\caption{The top 3 genes with prognostic impact in HNSCC (ranked by Bonferroni-adjusted \textit{P} values}
\label{tab:newTable1}
\resizebox{\linewidth}{!}{% \textwidth
\begin{tabular}{|l|l|l|c|c|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{} &
  \multicolumn{2}{c|}{} &
  \multicolumn{2}{c|}{Kaplan-Meier survival} &
  \multicolumn{2}{c|}{Univariate} &
  \multicolumn{2}{c|}{Multivariate} \\ \cline{4-9} 
\multicolumn{1}{|c|}{\multirow{-2}{*}{Gene ID}} &
  \multicolumn{2}{c|}{\multirow{-2}{*}{Gene Description}} &
  \begin{tabular}[c]{@{}c@{}}FDR\\ \textit{P} value\end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Bonferroni\\ \textit{P} value\end{tabular} &
  HR* &
  95\% CI &
  HR* &
  95\% CI \\ \hline
CAMK2N1 &
  \multicolumn{2}{l|}{\begin{tabular}[c]{@{}l@{}}calcium/calmodulin-\\ dependent protein\\ kinase II inhibitor 1\end{tabular}} &
  \num{2.9e-7} &
  0.002 &
  2.101 &
  1.572-2.809 &
  2.007 &
  1.490-2.704 \\ \hline
\rowcolor[HTML]{FFFFFF} 
{\color[HTML]{333333} IL19} &
  \multicolumn{2}{l|}{\cellcolor[HTML]{FFFFFF}{\color[HTML]{333333} interleukin 19}} &
  {\color[HTML]{333333} \num{3.7e-7}} &
  {\color[HTML]{333333} 0.002} &
  {\color[HTML]{333333} 0.472} &
  {\color[HTML]{333333} 0.351-0.635} &
  {\color[HTML]{333333} 0.459} &
  {\color[HTML]{333333} 0.340-0.619} \\ \hline
\rowcolor[HTML]{FFFFFF} 
{\color[HTML]{333333} FCGBP} &
  \multicolumn{2}{l|}{\cellcolor[HTML]{FFFFFF}{\color[HTML]{333333} \begin{tabular}[c]{@{}l@{}}Fc fragment of\\  IgG binding protein\end{tabular}}} &
  {\color[HTML]{333333} \num{1.2e-6}} &
  {\color[HTML]{333333} 0.008} &
  {\color[HTML]{333333} 0.484} &
  {\color[HTML]{333333} 0.359-0.653} &
  {\color[HTML]{333333} 0.496} &
  {\color[HTML]{333333} 0.366-0.674} \\ \hline
\multicolumn{9}{|l|}{} \\
\multicolumn{9}{|l|}{\multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Selection criteria:
1) Kaplan-Meier Bonferroni-adjusted \textit{P} \textless 0.05;
2) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5\end{tabular}}} \\ 
%\hline
\hline
\end{tabular}%
}
\end{table}

@@

%\subsubsection{Figure 3:h}
\begin{figure}[hp]
\centering
\includegraphics[width=14cm]{TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR-Figure3.pdf} % .png from PvalueplotKM_20genes_Bonf.pdf
\bcaption{Volcano plot of genes under survival analyses.}
{X axis: unadjusted \textit{P} value of Kaplan-Meier survival (-log10 transformed).
Y axis: multivariate hazard ratio from Cox proportional regression model.
Dotted line: significant Bonferroni corrected \textit{P} value. 
\textcolor{red}{Red dots} mark 10 genes (unvalidated), which impact on poor prognosis ($HR>=1.5$). \textcolor{green}{Green dots} mark 10 genes (unvalidated), which affect on better survival ($HR<=0.5$).}
\label{fig:figure3}
\end{figure}
% new figure of volcano plot: TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR.pdf, -log10(raw KM P-value) vs Cox multivariate HR
% X axis: "frequency" (number of uncorrected P-values less than 0.05 during Kaplan-Meier cutoff finding procedure). X axis: adjusted Kaplan-Meier P-value.

@@

%\subsubsection{Figure 4:h}
\begin{figure}[hp]
\centering
\includegraphics[width=15cm]{Figure_4_CAMK2N1_IL19.pdf}
\bcaption{Kaplan-Meier survival analyses, by cutoff finding.}
{(a) Kaplan-Meier plot of CAMK2N1 under optimal \textit{P} value, and (b) the cutoff is derived from cumulative \textit{P} value plot of CAMK2N1. (c) Kaplan-Meier plot of IL19 under optimal \textit{P} value, and (d) the cutoff is derived from cumulative \textit{P} value plot of IL19.}
\label{fig:figure4}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Tex
\usepackage{tikz-imagelabels} % for  tikz
\usepackage[]{caption} % bf
\newcommand{\bcaption}[2]{\caption{\textbf{#1} #2}}
\usepackage{outlines}
% mark in blue or red
\usepackage{xcolor}
\definecolor{asparagus}{rgb}{0.53, 0.66, 0.42}

@@

The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
The 967 genes were kept by criteria of uncorrected \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.5 or less than 0.5) (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b) multivariate plots). 
At the final step, a stringent criteria (Bonferroni \textit{P} value correction) was used to yield twenty candidates (see Figure \ref{fig:figure2}(c), (d)). 
% before validation
Among these candidates, ten overexpressed genes (symbol as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) are significantly associated with a poor prognosis of  \acrshort{os} (see Table \ref{tab:newTable1}). 
The other ten overexpressed genes (symbol as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival (see Table \ref{tab:newTable1}, with their gene name).
We made a volcano plot for 9416 genes by Kaplan-Meier \textit{P} value (less than 0.05, obtained during cutoff finding procedure) against the Cox hazard ratio (see Figure \ref{fig:hazards3}). %{fig:figure3}). 
The plot reveals that the top 20 genes (Bonferroni-adjusted \textit{P} $< 0.05$) are located on the peaks. At the same time, Cox's HR separated them on the two-side with prognostic impact.
% => after validation: The result showed six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are significantly associated with a poor prognosis of overall survival. Furthermore, the four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.

@@

%\subsubsection{Figure 2:h}
\begin{figure}[hp]
\centering
\includegraphics[width=14cm]{Figure2.pdf}
\bcaption{TCGA \acrshort{hnscc} Cox's hazard ratio and \textit{P} value plot.}
{(a) Univariate HR versus uncorrected \textit{P} value; (b) Multivariate HR versus uncorrected \textit{P} value; (c) Univariate HR versus Bonferroni corrected \textit{P} value; and (d) Multivariate HR versus Bonferroni corrected \textit{P} value.}
\label{fig:figure2}
\end{figure}

% tables 1  3
%%% tables
% Table1 = merged table 1and2
% wide table \usepackage{tabularx}
% makecell{}

@@

\begin{table}[hp]
\centering
\caption{The top 3 genes with prognostic impact in HNSCC}% (ranked by Bonferroni-adjusted \textit{P} values}
\label{tab:newTable1}
\resizebox{\linewidth}{!}{% \textwidth
\begin{tabular}{|l|l|l|c|c|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{} &
  \multicolumn{2}{c|}{} &
  \multicolumn{2}{c|}{Kaplan-Meier survival} &
  \multicolumn{2}{c|}{Cox Univariate} &
  \multicolumn{2}{c|}{Cox Multivariate} \\ \cline{4-9} 
\multicolumn{1}{|c|}{\multirow{-2}{*}{Gene ID}} &
  \multicolumn{2}{c|}{\multirow{-2}{*}{Gene Description}} &
  \begin{tabular}[c]{@{}c@{}}FDR\\ \textit{P} value\end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Bonferroni\\ \textit{P} value\end{tabular} &
  HR* &
  95\% CI &
  HR* &
  95\% CI \\ \hline
CAMK2N1 &
  \multicolumn{2}{l|}{\begin{tabular}[c]{@{}l@{}}calcium/calmodulin-\\ dependent protein\\ kinase II inhibitor 1\end{tabular}} &
  \num{2.9e-7} &
  0.002 &
  2.101 &
  1.572-2.809 &
  2.007 &
  1.490-2.704 \\ \hline
IL19 &
  \multicolumn{2}{l|} {interleukin 19} &
   \num{3.7e-7} &
   0.002 &
   0.472 &
   0.351-0.635 &
   0.459 &
   0.340-0.619 \\ \hline
FCGBP &
  \multicolumn{2}{l|}{\begin{tabular}[c]{@{}l@{}}Fc fragment of\\  IgG binding protein\end{tabular}} &
   \num{1.2e-6} &
   0.008 &
   0.484 &
   0.359-0.653 &
   0.496 &
   0.366-0.674 \\ \hline
\multicolumn{9}{|l|}{} \\
\multicolumn{9}{|l|}%{\multirow{-0}{*}
{\begin{tabular}[c]{@{}l@{}}
Selection criteria (fit all):\\
1) Kaplan-Meier Bonferroni-adjusted \textit{P} \textless 0.05;\\
2) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5 in TCGA cohort;\\
3) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5 in GSE65858 cohort
\end{tabular}
%}\\ % within \multirow
} \\ % within \multicolumn
\hline
\multicolumn{9}{|l|}{* Cox’s model: \textit{P} \textless 0.001} \\ \hline

\end{tabular}%
}
\end{table}

@@

%\subsubsection{Figure 3:h}
\begin{figure}
    \centering
    \includegraphics[width=13cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_top3FDRKM.pdf}
    \bcaption{Volcano plot of genes under survival analyses of TCGA HNSCC.}{
%X axis: unadjusted \textit{P} value of Kaplan-Meier survival (-log10 transformed).
%Y axis: multivariate hazard ratio from Cox proportional regression model.
%Dotted line: significant Bonferroni corrected \textit{P} value. 
%\textcolor{red}{Red dots} mark 10 genes (unvalidated), which impact on poor prognosis ($HR>=1.5$). \textcolor{green}{Green dots} mark 10 genes (unvalidated), which affect on better survival ($HR<=0.5$).
    This cohort has been applied for exploration of the candidate biomarkers.
    Total 9416 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05.
    \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the other 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.6$.\\
    Remarks:\\
    \textcolor{red}{Red spots}: $HR > 1.0$;
    \textcolor{green}{Green spots}: $HR < 1.0$;\\
    X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);\\
    Y-axis: HR of Cox proportional hazard regression model\\
    }
%\label{fig:figure3}
\label{fig:hazards3} %TCGA volcano
\end{figure}
% new figure of volcano plot: TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR.pdf, -log10(raw KM P-value) vs Cox multivariate HR
% X axis: "frequency" (number of uncorrected P-values less than 0.05 during Kaplan-Meier cutoff finding procedure). X axis: adjusted Kaplan-Meier P-value.

@@

%\subsubsection{Figure 4:h}
% *** Adjusted P value = 0.002 ; drawing by tikz
% https://tex.stackexchange.com/questions/9559/drawing-on-an-image-with-tikz

%font code: Computer Modern Sans Serif		cmss

\begin{figure}[hp]

% TCGA FDR Pvalue of CAMK2N1 (1.628308e-05), IL19 ( 6.543871e-06), FCGBP (4.827833e-05)
\setlength{\unitlength}{1cm}
\begin{picture}(15, 20) %(1,0.55038404)%
\centering
  \put(0,0){\includegraphics[width=14cm]{Figure_4_CAMK2N1_IL19_FCGBP.pdf}}%
  \put(2.5, 14.3){\fontfamily{qcr}\selectfont
  \tiny *\textit{P} = \num{1.63e-05}}%CAMK2N1
    \put(2.5, 9.45){\fontfamily{qcr}\selectfont
  \tiny *\textit{P} = \num{6.54e-06}}%IL19
    \put(2.5, 4.55){\fontfamily{qcr}\selectfont
  \tiny *\textit{P} = \num{4.83e-05}}%FCGBP

%\begin{annotationimage}{width=15cm}{Figure_4_CAMK2N1_IL19_FCGBP.pdf}
%\includegraphics[width=15cm]{Figure_4_CAMK2N1_IL19.pdf}
%\draw[annotation left = {Aries at 0.3}]

%\end{annotationimage}
\end{picture}%

\bcaption{Kaplan-Meier survival analyses, by cutoff finding.}
{The Kaplan-Meier curves of (a) CAMK2N1, (c) IL19, and (e) FCGBP under optimal \textit{P} value. 
%((b) the cutoffs derived from it's cumulative \textit{P} value plot).
%(c) Kaplan-Meier plot of IL19 under optimal \textit{P} value;
%((d) the cutoffs derived from it's cumulative \textit{P} value plot).
%(e) Kaplan-Meier plot of FCGBP under optimal \textit{P} value.\\
The cutoffs, in the cumulative \textit{P} value plots of (b) CAMK2N1, (d) IL19, and (f) FCGBP, respectively,
shows that over 50\% of those unadjusted \textit{P} values are below 0.001 derived by sliding-window cutoff finding procedure.\\
* \textit{P}: Adjusted \textit{P} value by \acrfull{fdr}
}
\label{fig:figure4}
\end{figure}
